%-------------------------
% Resume in LaTeX
% Author: Syed Ali Raza
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins — tight but readable
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries\color[RGB]{31,78,121}
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-1pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-4pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, itemsep=-1pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Syed Ali Raza} \\ \vspace{3pt}
    \small
    \faPhone\ +1 (647) 996-4892 \enspace
    \faEnvelope\ \href{mailto:ali-raza@live.ca}{ali-raza@live.ca} \enspace
    \faGlobe\ \href{https://ali-raza.ca}{ali-raza.ca} \enspace
    \faGithub\ \href{https://github.com/razas32}{github.com/razas32} \enspace
    \faLinkedin\ \href{https://linkedin.com/in/razas32}{linkedin.com/razas32}
\end{center}
\vspace{-6pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Bachelor of Computer Engineering \& Management (CO-OP)}{Sep 2020 -- June 2025}
      \resumeItemListStart
        \resumeItem{Recipient of the 2020 McMaster Entrance Honor Scholar Award}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt, topsep=0pt]
    \small{
      \item \textbf{Languages:} C++, C, C\#, Verilog, Python, Java, JavaScript, CSS, TypeScript, SQL, MATLAB
      \item \textbf{Frameworks:} React.js, Chrono, TensorFlow, Tkinter, NumPy, SciPy, Pillow, Matplotlib, Pandas, PyTorch
      \item \textbf{Tools:} Git, GitHub, Quartus Prime, Simulink, ModelSim, Azure, AWS, Unreal Engine, PSpice, Salesforce, Visual Studio, Kubernetes, Docker, Tableau
      \item \textbf{Relevant Courses:} Algorithm Design \& Analysis, Logic Design, Software Development, Microprocessor Systems, Advanced Probability, Electronic Circuits \& Devices II, Digital Systems Design, Control Systems, Communication Systems, Computer-Aided Engineering, Computer Architecture
    }
\end{itemize}
\vspace{-4pt}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Analyst}{May 2023 -- Aug 2023}
      {Vanguard Financial}{Mississauga, ON}
      \resumeItemListStart
        \resumeItem{Managed financial records for 30+ business clients using Python \& SQL to enhance data manipulation, analysis, and visualization across large financial datasets.}
        \resumeItem{Automated bank statement reconciliation via Python, processing \textasciitilde1,000 transactions/week at \textgreater99\% accuracy; built complementary VBA macros to streamline Excel reporting.}
        \resumeItem{Contributed to deploying a new SQL database system, overseeing data migration and improving organizational data integrity and query performance.}
      \resumeItemListEnd

    \resumeSubheading
      {B2B Marketing Manager}{July 2022 -- Nov 2022}
      {The Rec Source}{GTA, ON}
      \resumeItemListStart
        \resumeItem{Drove sales initiatives for customized workforce solutions across the GTA, travelling to company warehouses and securing 4 high-value contracts exceeding \$100K each.}
        \resumeItem{Initiated and led meetings with HR managers across Ontario, fostering strong client relationships while overseeing and mentoring a team of 3 marketing representatives.}
      \resumeItemListEnd

    \resumeSubheading
      {B2C Sales Consultant}{May 2022 -- Aug 2022}
      {Go Sales}{GTA, ON}
      \resumeItemListStart
        \resumeItem{Secured 68 TELUS smart home security contracts via door-to-door marketing, achieving a \textasciitilde2\% conversion rate and exceeding quarterly sales targets by 44\%.}
        \resumeItem{Engaged \textasciitilde100 prospects daily, generating 10\% average qualified leads through effective communication and a consultative understanding of client needs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Franky --- Rocket League ML Bot} $|$ \emph{Python, PyTorch, RLGym, NumPy}}{Jan 2022 -- Apr 2022}
      \resumeItemListStart
        \resumeItem{Built an autonomous bot using RLGym with engineered behaviors (positioning, velocity, movement) blended with high-level game strategy.}
        \resumeItem{Applied deep reinforcement learning via PyTorch with custom state logic for real-time decision making across diverse in-game scenarios.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Software Defined Radio} $|$ \emph{Linux, C++, Python, Gnuplot}}{Feb 2024 -- Apr 2024}
      \resumeItemListStart
        \resumeItem{Developed DSP algorithms for mono/stereo FM demodulation and RDS processing in a team of four; implemented in C++ and validated with Python on a Raspberry Pi.}
        \resumeItem{Optimized throughput using multithreading to meet strict real-time latency constraints within the Linux ecosystem.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Hardware-based Image Decompressor} $|$ \emph{Verilog, Quartus Prime, ModelSim}}{Oct 2023 -- Dec 2023}
      \resumeItemListStart
        \resumeItem{Designed a real-time Verilog FSM decompression pipeline handling YUV-to-RGB conversion within tight hardware resource and latency budgets.}
        \resumeItem{Managed UART data flow to an Altera DE2-115 FPGA for SRAM decoding and storage, then routed output to a VGA controller for live display.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{LIDAR Spatial Mapper} $|$ \emph{C, Python, NumPy, Open3D}}{Feb 2023 -- Apr 2023}
      \resumeItemListStart
        \resumeItem{Engineered a 3D scanner using a VL531X ToF sensor, 28BYJ-48 stepper motor, and MSP432E401Y microcontroller for enclosed-area spatial mapping.}
        \resumeItem{Implemented I2C \& UART protocols for sensor-to-PC transfer; converted distance data to Cartesian coordinates and rendered 3D point clouds with Open3D.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Model Pacemaker} $|$ \emph{MATLAB, Python, Simulink}}{Sep 2022 -- Dec 2022}
      \resumeItemListStart
        \resumeItem{Co-developed a digital pacemaker simulation in a team of four using MATLAB Simulink, implementing atrial/ventricular pacing and multi-mode sensing algorithms.}
        \resumeItem{Designed a GUI in Python with Tkinter and pySerial for real-time system interfacing and operational parameter configuration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}
